Manuscript

### 2022-08-31 Manuscript.Rmd
cleaning up MS

![Individual regression estimates when no relationship exists across the hypothetical environmental gradient. The methods are separated by rows, and the left and right column show relationships which were non-significant and significant, respectively. The individual regressions coefficients are colored-coded to indicate positive and negative relationship estimates. ](figures/static_b_lambda_spaghetti.png)

@@

![Distribution of the estimated relationship for each method. Here, $\lambda$ varied from -1.9 to -2.1, with a known relationaship of -0.1 across the gradient indicated by the dashed vertical line.](figures/PLB_sim_small_relationship_density.png)

![Linear regressions across the hypothetical gradient when lambda varies from -1.9 to -2.1. Each method is displayed in the rows, and the left colum shows the non-significant estimates, while the right column shows the relationships which were signficant ($\beta_1$ coefficient p-value \< 0.05). The colors indicate when the beta coefficient estimate was negative (pink) and when it was positive (purple).](figures/small_lambda_spaghetti.png)

@@

![Distribution of relationship coefficient estimates. Vertical line is the known relationship. All methods under estimate the value, but the mean magnitude and distribution of values is greater for the ELBn and NAS methods.](figures/shallow_lambda_relationship_density.png)

>>>>

![Distribution of all lambda estimates across sites when there is no relationaship. The coeficient estimates for the binning methods tend to be shallower and have wider distributions than the MLE method.  ](figures/PLB_static_b_est_b_density.png)

![Individual regression estimates when no relationship exists across the hypothetical environmental gradient. The methods are separated by rows. The median for all methocs is approximately zero, but the distribution for the MLE method is narrower than the two binning methods. ](figures/PLB_static_b_relationship_density.png)

@@

![Distribution of the estimated relationship for each method. Here, $\lambda$ varied from -1.9 to -2.1, with a known relationaship of -0.1 across the gradient indicated by the dashed vertical line. The distribution of relationship estimates was approximately centered at the known relationship for all methods, with a narrower distribution observed for the MLE estimates. ](figures/PLB_sim_small_relationship_density.png)

@@

![Distribution of relationship coefficient estimates. Vertical line is the known relationship. All methods under estimate the value, but the mean magnitude and distribution of values is greater for the ELBn and NAS methods.](figures/PLB_shallow_lambda_relationship_density.png)
